---
title: "Exercise: Explore, Clean, and Wrangle Data”"
author: "Karrin"
format: html
---

## About the data

SBC LTER: Reef: Abundance, size and fishing effort for California Spiny Lobster (Panulirus interruptus), ongoing since 2012.  Data on abundance, size and fishing pressure of California spiny lobster (Panulirus interruptus) are collected along the mainland coast of the Santa Barbara Channel.

## Setup

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```


## Read and explore data


```{r}
# Read in data
lobster_abundance <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=f32823fba432f58f66c06b589b7efac6")

lobster_traps <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=66dd61c75bda17c23a3bce458c56ed84")
```

```{r}
summary(lobster_abundance)
summary(lobster_traps)
```


```{r}
head(lobster_abundance)
head(lobster_traps)
```

```{r}
colnames(lobster_abundance)
colnames(lobster_traps)
```


## Exercise 1

## Exercise 2 

## Exercise 3 

## Exercise 4 

## Exercise 5 

## Exercise 6 